Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-10 Manuscript/FLPhish(Trans).tex
图片label，size，尺寸，位置修改

\begin{figure*}[!htp]
  \centering
    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
    \subfigure[$q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
  \label{fig_exp_mnist-reputation}
  \vspace{0.2in}
\end{figure*}

\begin{figure*}[!htp]
  \centering
    \subfigure[$q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
    \subfigure[$q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
    \subfigure[$q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
    \subfigure[$q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on Fashion-MNIST on different imbalance degrees.}
  \label{fig_exp_fashion_reputation}
  \vspace{0.2in}
\end{figure*}

\begin{figure*}[!htp]
  \centering
    \subfigure[{$q=$}0.1]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
    \subfigure[{$q=$}0.2]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
    \subfigure[{$q=$}0.5]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
    \subfigure[{$q=$}0.8]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on CIFAR-10 on different imbalance degrees.}
  \label{fig_exp_cifar_reputation}
  \vspace{0.2in}
\end{figure*}

@@

@@

  \subsection{Performance Comparison under Random Attacks}
  From Fig. \ref{fig_exp_extreme}-\ref{fig_table_cifar_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2). We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do. While we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_cifar_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5). While, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2), and FLPhish-weight stood still against the random Byzantine attacks. The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.

  \begin{figure*}[!htp]
    \centering
    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
    \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Imbalance Degrees under Random Attack.}
    %\label{fig_table_mnist_random}
  \end{figure*}

  \begin{figure}[ht]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
    \\
    \caption{Accuracy values on MNIST under Random Attack.}
    \label{fig_table_mnist_random}
    \vspace{0.2in}
  \end{figure}
  \begin{figure}[!htp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
    \\
    \caption{Accuracy values on Fashion-MNIST under Random Attack.}
    \label{fig_table_fashion_random}
    \vspace{0.2in}
  \end{figure}
  \begin{figure}[!htp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on CIFAR-10 under Random Attack.}
    \label{fig_table_cifar_random}
    \vspace{0.2in}
  \end{figure}

@@

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the Experiments. The experiment results are shown in Fig. \ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted}. We can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8. The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID. The performance of the FLPhish-threshold with a threshold of 0.5 rapidly falls in this case. When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation. The rise of imbalance degree brings an explosive decline to the global model's accuracy. The accuracy of the global model under the FLPhish-threshold of threshold 0.5 stays 0.1 in the whole learning process. It means that the FLPhish-threshold of threshold 0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid. We can see that the FLPhish-threshold of threshold 0.2 outperforms others. When the distribution becomes non-IID, the threshold of FLPhish-threshold should be set to a lower value to avoid a high false-negative rate. In the experiment of MNIST, it should be set to 0.2. Meanwhile, the performance of FLPhish-weight remains stable under different imbalance degrees.

      \begin{figure}[tp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
    \\
    \caption{Accuracy values on MNIST under Untargeted Attack.}
    \label{fig_table_mnist_untargeted}
    \vspace{0.2in}
  \end{figure}
  \begin{figure}[tp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
    \\
    \caption{Accuracy values on Fashion-MNIST under Untargeted Attack.}
    \label{fig_table_fashion_untargeted}
    \vspace{0.2in}
  \end{figure}
  \begin{figure}[tp]
    \centering
      \subfigure[$p\,0.5$ \& Different $q$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
      \subfigure[$q\,0.2$ \& Different $p$]{\includegraphics[width=0.24\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on CIFAR-10 under Untargeted Attack.}
    \label{fig_table_cifar_untargeted}
    \vspace{0.2in}
  \end{figure}

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Figure. \ref{fig_table_mnist_untargeted}-\ref{fig_table_cifar_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean, and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintains a high level of performance as the portion grows. Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discards them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients in aggregation procedures. Furthermore, the data show that FLPhish-threshold with a 0.1 threshold performs worse than the other two. This is since the 0.1 threshold is far too low to adequately detect Byzantine clients. Though the Byzantine attackers will try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they will also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish-threshold. As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks will increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish-weight shows stable performance whenever the fractions of Byzantine clients are.

>>>>

\begin{figure*}[!htp]
  \centering
    \subfigure[MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
    \subfigure[MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
    \subfigure[MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
    \subfigure[MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}

    \subfigure[Fashion-MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
    \subfigure[Fashion-MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
    \subfigure[Fashion-MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
    \subfigure[Fashion-MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}

    \subfigure[CIFAR-10 {$q=0.1$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
    \subfigure[CIFAR-10 {$q=0.2$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
    \subfigure[CIFAR-10 {$q=0.5$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
    \subfigure[CIFAR-10 {$q=0.8$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
  \label{fig_exp_reputation}
  \vspace{0.2in}
\end{figure*}

@@

  \begin{figure*}[!htp]
    \centering
    \subfigure[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
    \subfigure[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
    \subfigure[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Imbalance Degrees under Random Attack.}
    \label{fig_table_imbalances_random}
  \end{figure*}

  \begin{figure*}[!htp]
    \centering
    \subfigure[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
    \subfigure[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
    \subfigure[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Byzantine Fractions under Random Attack.}
    \label{fig_table_byzantines_random}
  \end{figure*}

@@

  \subsection{Performance Comparison under Random Attacks}
  From Fig. \ref{fig_exp_extreme}-\ref{fig_table_byzantines_random}, we can see that random Byzantine attacks have poor performance against FLPhish-weight and FLPhish-threshold (threshold=0.1, 0.2). We refer from the result that a random Byzantine attack has a drawback that it can not gather its influence at one data point as untargeted Byzantine attackers do. While we can see that it has good results in attacking FLPhish-threshold(threshold=0.5) in the CIFAR-10 dataset. From Fig. \ref{fig_exp_reputation}, we can see that the reputation of benign clients in CIFAR-10 experiments rapidly falls under the threshold of 0.5 due to the complexity of the tasks. With the increase of imbalance degree value $q$, the reputation of the benign clients falls more rapidly in the experiments of the CIFAR-10 dataset than in the experiments of the MNIST and the Fashion-MNIST dataset. As benign clients' reputations in the experiments of the CIFAR-10 dataset become under the threshold $\tau$ of 0.5, they are identified as malicious Byzantine clients as well. As many benign clients are falsely identified as Byzantine attackers, the FL server lacks enough trusted FL clients to assist the aggregation, therefore causing a bad performance of FLPhish-threshold (threshold=0.5). While, we can see that FLPhish-threshold (threshold=0.1), FLPhish-threshold (threshold=0.2), and FLPhish-weight stood still against the random Byzantine attacks. The results indicate that the value of the threshold $\tau$ should be considered carefully in the application in some complex tasks.

  \begin{figure*}[!htp]
    \centering
    \subfigure[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
    \subfigure[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
    \subfigure[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Imbalance Degrees under Untargeted Attack.}
    \label{fig_table_imbalances_untargeted}
  \end{figure*}

  \begin{figure*}[!htp]
    \centering
    \subfigure[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
    \subfigure[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
    \subfigure[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Byzantine Fractions under Untargeted Attack.}
    \label{fig_table_byzantines_untargeted}
  \end{figure*}

@@

    \subsubsection{\ul{Performance Comparison with Different Distributions}} We evaluate our FLPhish-threshold and FLPhish-weight under the condition where the Byzantine client portion is a fixed value of 0.5 and distribution imbalance value $q$ is different across the Experiments. The experiment results are shown in Fig. \ref{fig_table_imbalances_untargeted}. We can observe that both the FLPhish-threshold and FLPhish-weight outperform baseline until the imbalance degree $q$ reaches 0.8. The imbalance degree $q$ of 0.8 means that the distribution of data becomes extremely non-IID. The performance of the FLPhish-threshold with a threshold of 0.5 rapidly falls in this case. When facing the distribution of imbalance degree $q=0.8$, each client performs badly, bringing a decline to its reputation. The rise of imbalance degree brings an explosive decline to the global model's accuracy. The accuracy of the global model under the FLPhish-threshold of threshold 0.5 stays 0.1 in the whole learning process. It means that the FLPhish-threshold of threshold 0.5 identifies all the clients as Byzantine clients, making the aggregation process invalid. We can see that the FLPhish-threshold of threshold 0.2 outperforms others. When the distribution becomes non-IID, the threshold of FLPhish-threshold should be set to a lower value to avoid a high false-negative rate. In the experiment of MNIST, it should be set to 0.2. Meanwhile, the performance of FLPhish-weight remains stable under different imbalance degrees.

    \subsubsection{\ul{Performance Comparison with Different Fractions of Byzantine Clients}} Different fractions of Byzantine clients are taken into account as well. Figure. \ref{fig_table_byzantines_untargeted} shows that the accuracy for FedAvg, Median, Trimmed Mean, and Ensemble FL without any defense mechanisms begins to fall rapidly when the Byzantine portion reaches nearly 50\%. Furthermore, FedAvg, Median, and Trimmed Mean perform extremely invalidly (the accuracy falls below 1\%) when encountered with high fractions of Byzantine attackers. In comparison, FLPhish's (including FLPhish-threshold and FLPhish-weight) performance under various thresholds maintains a high level of performance as the portion grows. Both FLPhish-threshold and FLPhish-weight effectively detect Byzantine clients and accurately discards them from the aggregation process. The global model can be successfully trained without the involvement of Byzantine clients in aggregation procedures. Furthermore, the data show that FLPhish-threshold with a 0.1 threshold performs worse than the other two. This is since the 0.1 threshold is far too low to adequately detect Byzantine clients. Though the Byzantine attackers will try to make the right predictions of the public dataset and then send the opposite wrong predictions to the FL server. But they will also make wrong predictions first and coincidentally transfer the opposite right predictions to the FL server. Thus the reputation values of some Byzantine clients, in particular, can exceed 0.1. It indicates that if the threshold is not well set, Byzantine clients can avoid being detected by FLPhish-threshold. As the fractions of Byzantine clients go over the threshold of 50\%, the harm brought by untargeted Byzantine attacks will increase rapidly for they outnumber the fractions of the benign clients. In the meantime, FLPhish-weight shows stable performance whenever the fractions of Byzantine clients are.
